Browsing the Web of Factual Claims

### 2008-09-20 papers/web_of_ideas/web_of_ideas.tex
Submitted version. Minor changes

Conventional web browsers allow a user to look at pages and follow links between them; however when a user browses the web it is often not the pages themselves that they are looking for but claims about the world that are contained on those pages. A page may contain claims that are contradicted by other pages, or contain one interesting new claim hidden in a sea of claims that the user has already read. If a user is to form an accurate opinion about a topic then they may have to spend considerable time gathering information from many disconnected pages scattered across the web.

@@

Part of the problem is that conventional web browsing tools require the user to browse by looking at pages, when it is often not the pages themselves that the user is interested in but the factual claims contained within them. While a web page will typically contain links to other articles, these typically only reference a small proportion of the other pages that discuss the topic, and are unlikely to include sources that disagree with the author. The best arguments supporting or opposing a claim may be distributed across a large number of disconnected pages, making it difficult for a user to assemble an argument from the pages on the web. The root of the problem is that the web is structured around where knowledge is coming from (pages written by particular authors) rather than what knowledge is about (the ideas contained on the pages). While this makes it easier for add knowledge to the web, it makes it hard for users to collate all the knowledge available on a topic.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/summary_graph.png}
	\caption{Think link connects claims to each other and to web snippets}
	\label{summarygraph}
	\end{center}
\end{figure}

In this paper we present Think Link, a tool that overlays a new network of links over the existing web, connecting snippets of text to snippets elsewhere on the web that make related claims. Think Link maintains a central shared ``claim graph'' (Figure~\ref{summarygraph}) containing claims made on the web, their supporting and opposing relationships to each other, and the snippets that make these claims. When a user views a web page, Think Link highlights snippets that have been identified as making factual claims, with the highlight color indicating whether other sources have been found that disagree with the claim. If a user clicks on such a snippet then they will see a ``claim browser'' (Figure~\ref{claimview}) that allows them to see other claims made on the web that support or oppose the claim the snippet makes, and snippets elsewhere on the web that make these other claims.

@@

Another key difference between Think Link and a Wiki is that Think Link pulls the whole web into its graph of connected claims. A user can use Think Link to investigate claims they read on arbitrary web sites, without having to restrict their browsing to a single wiki site.

@@

One of the goals of Think Link is that people should be able to browse information on the web through the ideas being expressed. This is a goal that is shared with several other projects. Kolak and Schilit~\cite{quotations} find places where a passage is repeated in several documents (usually a quotation) and allows users to navigate from such a passage to all other documents where that passage is quoted. Idea Navigation~\cite{ideanavigation} uses a natural language parser to identify subject-verb-object assertions in documents and then allows users to search for browse the assertions in a document corpus. ScentHighlights~\cite{scenthighlights} identifies sections of text that you might find interesting and highlights them for you. ScentTrails~\cite{scenttrails} identifies links to documents that you might find interesting and makes them bigger. Unlike Think Link, these tool attempt to extract text of interest automatically, rather than relying on users to identify and connect interesting factual claims.

@@

Think Link is a tool that overlays a web of factual claims on the existing web (Figure~\ref{summarygraph}). As a user browses the web, Think Link highlights snippets of text that have been identified as making factual claims. If a user clicks on a highlighted snippet then Think Link will display an interface that allows the user to easily find snippets on other pages that make related claims (Figure~\ref{claimview}). Our intention is that Think Link allows a user to easily access the best arguments for and against a claim that can be found on the web, and allows users to more easily evaluate the truth of claims that they read.

Think Link has a global graph of factual claims that is shared by all users (Figure~\ref{summarygraph}). This graph is managed like a Wiki, allowing any user to add new claims or snippets. As a user browses the web, they can identify snippets that make claims that are interesting or controversial and link them into the global claim graph.

@@

\begin{itemize}
\item {\bf a claim} (\includegraphics[width=0.3cm]{../images/lightbulb_off.png}) is a factual claim about the world that may be true or false. For example ``Global warming is man made''. A claim may support or oppose other claims. Claims are written as raw English\footnote{though one can imagine supporting other languages in the future} text and Think Link does not try to understand what they mean semantically.
\item {\bf a snippet} (\includegraphics[width=0.3cm]{../images/comment.png}) is a section of text on a web page that asserts or assumes the truth of a particular claim. Many snippets may assert the same claim and users are encouraged to re-use existing claims rather than creating new ones when creating new snippets.
\item {\bf a topic} (\includegraphics[width=0.3cm]{../images/folder_grey.png}) is a thing that claims can be about. For example ``Global Warming'', or ``Computer Science''. A claim can have one or more topics that it is about, and a topic can have one or more more general topics. Topics are used both to organize, and to disambiguate claims. For example ``Bush'' can mean either ``George H W Bush'', ``George W Bush'', ``Vannevar Bush'', ``Kate Bush'', ``The Rock Band Bush'', or just ``A Bush''. Associating a claim with a topic allows one to write shorter claims without worrying about being ambiguous. A topic can itself by disambiguated by having a super-topic.
\end{itemize}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/claimbrowse_diagram.png}
	\caption{The claim browser visualizes the claim graph}
	\label{claimbrowse_diagram}
	\end{center}
\end{figure}
\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/claimbrowse_zoom.png}
	\caption{Close up of a list of supporting claims}
	\label{claimbrowse_zoom}
	\end{center}
\end{figure}

@@

After several iterations, we settled on an interface that is a dynamically reorganizing graph laid out like an outliner. Like other dynamically reorganizing graphs, the interface is arranged around the currently selected node, and when a new node is selected the interface animates to surround the newly selected node with objects to relate to it. Like an outliner, the nodes that relate to the selected node are listed vertically below the selected node, each on their own line, and grouped by category.

@@

@@

Users see a claim browser in three different places. The {\bf organizer} contains two claim browsers, to help users use drag and drop to create connections (Figure~\ref{fig:claimbrowser}). {\bf The Popup Browser} shows one claim browser in a reduced-size window and is used to quickly investigate a claim found on a web page (Figure~\ref{claimview}). The {\bf Claim Selector} shows a claim browser, together with the text of a new snippet, and is used to identify the claim that a snippet is making (Figure~\ref{snipsavecrop}).

@@

There are several reasons a user may wish to add a snippet to Think Link. It may be that they find the snippet useful and may want to refer to it again in the future. It may be that they disagree with the claim the snippet is making, and want to alert other readers to the fact that there are opposing arguments, it may be that they think the claim argues a point well and want to be able to use it to make an argument, or it may be that they agree with the claim and want to provide easy access to evidence elsewhere that backs it up.

@@

Since much of Think Link's utility comes from linking snippets together, it is important that to encourage users to reuse existing claims rather than creating new ones, and that when users do create new claims they connect them to existing claims and existing topics. Motivated by this, we designed the claim selection window to make it easier to pick out an existing claim than to create a new one. Moreover, one cannot create a new claim without connecting it to an existing topic or an existing claim. To create a new claim, one navigates to a topic that the claim is about, or a claim that the new claim supports or opposes, and then clicks on the (\includegraphics[width=0.3cm]{../images/add.png}) button on the list that one wishes to add the new claim to. For example, if the new claim opposes an existing claim, then one clicks the (\includegraphics[width=0.3cm]{../images/add.png}) button on the ``opposed by'' heading for the existing claim. This is an intentionally different model to that used by ad-hoc tag-based systems such as Del.icio.us and Flickr.com. This is because in bookmarking or image storing systems it is not so important that duplicates be avoided and that objects be well connected. In practice, it is inevitable that duplicates claims and topics will sometimes be created. When this happens, a user can mark them as being identical using the same techniques used to create supporting and opposing connections.

@@

Like Wikipedia~\cite{wikipedia}, Think Link allows any user to improve the information in the claim graph. The claim graph is shared between all users and editable by anyone. Any user can add new snippets, create new claims, create new topics, or establish new relationships between these objects. One can think of Think Link as being rather like a Wiki in which all the content is clipped from existing sources and links are created from those sources back to the wiki.

@@

Unlike a Wiki, in which users can edit and delete information produced by others, and history is used to revert abusive changes, Think Link's ``append-only, collaborative filtering'' approach only allows users to add information --- either new objects, or ratings for those objects. The hope is that over time ratings should converge to a steady state and edit wars should be avoided. It would not be practical for a wiki to take this approach as their data is human-readable text, rather than a weighted graph; indeed Think Link has to fall back to the ``edit and keep history'' approach to allow users to rename claims.

@@

Our user study participants identified several reasons why they would want to mark up factual claims in documents they found. The most common reason people gave for identifying and organizing factual claims was if the person was writing an article or researching a topic and wanted to keep track of the information they had found. One user (who was an active blogger) also expressed an interest in finding and marking up instances of claims that he disagreed with, so that readers would see the arguments highlighted in red and be directed to the counter-arguments. The same user also expressed an interest in marking up claims in documents he had made in his own articles so that readers could quickly see the evidence he had found in support of his claims.

@@

For the second study, we recruited 6 paid participants. Four were female and two were male. Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the semester meant that five of the participants were students. Since the second group was different demographically to the first group, it was not possible to make a direct comparison between their behaviors.

In the second study we were more confident about the usability of our tool and so we decided to tell them nothing about how to use it. We gave each user a brief introduction to the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it. The first task was to look at a selection of web pages that already had highlights and explore the interface while thinking aloud about what they saw. The second task was to identify claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated the claim graph with. Participants were shown an interface that is largely identical to that described earlier in this paper.

@@

Users would often encounter a snippet that could be interpreted as making several interesting claims, and were unsure about what to do in such circumstances. Sometimes users would deal with this by writing a compound claim like ``Global Warming will cause X and Y''. While users could mark up the same snippet as making multiple claims. Users seemed to find this confusing, suggesting that we may want support in the snippet creation interface for picking several claims that a snippet is making.

@@

For the second study, we used the interface described earlier in this paper, which uses the same claim browser interface used for exploring the claim graph. We found that users of this interface had no difficulty distinguishing between claims and topics and were more likely to reuse existing claims and topics. We theorized that part of the reason for increased reuse was that, because users could see the claim graph they were creating, they felt more motivation to keep it ``tidy'' by reusing existing claims.

@@

Think Link is designed to be used as a social tool in which large numbers of people collaborate to find large numbers of claims and snippets about interesting topics. Since our graph and user base are currently small we have not yet evaluated how Think Link works when data sets are huge, many users are concurrently editing data, and some users are malicious.

>>>>

Conventional web browsers allow a user to look at pages and follow links between them; however when a user browses the web it is often not the pages themselves that they are looking for, but claims about the world that are contained on those pages. A page may contain claims that are contradicted by pages elsewhere on the web, or for which better arguments can be found in other places. If a user is to form an accurate opinion about a topic then they may have to spend considerable time gathering information from many disconnected pages scattered across the web.

@@

Part of the problem is that conventional web browsers present the web as a network of connected pages, when it is often the case that what the user is really interested in is the factual claims made by those pages, and the connections between those claims. While a web page will typically contain links to other articles, these typically only reference a small proportion of the other pages that discuss the topic, and are unlikely to include sources that disagree with the author. The best arguments supporting or opposing a claim may be distributed across a large number of disconnected pages, making it difficult for a user to assemble an argument from the pages on the web. The root of the problem is that the web is structured around where knowledge is coming from (pages written by particular authors) rather than what knowledge is about (the ideas contained on the pages). While this makes it easier for users to add knowledge to the web, it makes it hard for users to collate all the knowledge available on a topic.

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=7.7cm]{../screenshots/summary_graph.png}
	\caption{Think link connects claims to each other and to web snippets}
	\label{summarygraph}
	\end{center}
\end{figure}

In this paper we present Think Link, a tool that overlays a new network of links over the existing web, connecting snippets of text to snippets elsewhere on the web that make related claims. Think Link maintains a central shared ``claim graph'' (Figure~\ref{summarygraph}) containing claims made on the web, their supporting and opposing relationships to each other, and the snippets that make these claims. When a user views a web page, Think Link highlights snippets that have been identified as making factual claims, with the highlight color indicating whether other sources have been found that disagree with the claim. If a user clicks on a snippet then they will see a ``claim browser'' (Figure~\ref{claimview}) that allows them to see other claims made on the web that support or oppose the claim the snippet makes, and snippets elsewhere on the web that make these other claims.

@@

Another key difference between Think Link and a wiki is that Think Link pulls the whole web into its graph of connected claims. A user can use Think Link to investigate claims they read on arbitrary web sites, without having to restrict their browsing to a single wiki site.

@@

One of the goals of Think Link is that people should be able to browse information on the web through the ideas being expressed. This is a goal that is shared with several other projects. Kolak and Schilit~\cite{quotations} find places where a passage is repeated in several documents (usually a quotation) and allow users to navigate from such a passage to all other documents where that passage is quoted. Idea Navigation~\cite{ideanavigation} uses a natural language parser to identify subject-verb-object assertions in documents and then allows users to search for browse the assertions in a document corpus. ScentHighlights~\cite{scenthighlights} identifies sections of text that you might find interesting and highlights them for you. ScentTrails~\cite{scenttrails} identifies links to documents that you might find interesting and makes them bigger. Unlike Think Link, these tool attempt to extract text of interest automatically, rather than relying on users to identify and connect interesting factual claims.

@@

Think Link is a tool that overlays a web of factual claims on the existing web (Figure~\ref{summarygraph}). As a user browses the web, Think Link highlights snippets of text that have been identified as making factual claims. If a user clicks on a highlighted snippet, Think Link will display an interface that allows the user to easily find snippets on other pages that make related claims (Figure~\ref{claimview}). Think Link allows a user to easily access the best arguments for and against a claim that can be found on the web, and allows users to more easily evaluate the truth of claims that they read.

Think Link has a global graph of factual claims that is shared by all users (Figure~\ref{summarygraph}). This graph is managed like a wiki, allowing any user to add new claims or snippets. As a user browses the web, they can identify snippets that make claims that are interesting or controversial and link them into the global claim graph.

@@

\begin{itemize}
\item {\bf a claim} (\includegraphics[width=0.3cm]{../images/lightbulb_off.png}) is a factual claim about the world that may be true or false. For example ``Global warming is man made''. A claim may support or oppose other claims. Claims are written as raw English\footnote{though one can imagine supporting other languages in the future} text and Think Link does not try to understand what they mean semantically.
\item {\bf a snippet} (\includegraphics[width=0.3cm]{../images/comment.png}) is a section of text on a web page that asserts or assumes the truth of a particular claim. Many snippets may assert the same claim and users are encouraged to re-use existing claims rather than creating new ones when creating new snippets.
\item {\bf a topic} (\includegraphics[width=0.3cm]{../images/folder_grey.png}) is a thing that claims can be about. For example ``Global Warming'', or ``Computer Science''. A claim can be about one or more topics, and a topic can have one or more more general topics. Topics are used to organize and disambiguate claims. For example ``Bush'' can mean either ``George H W Bush'', ``George W Bush'', ``Vannevar Bush'', ``Kate Bush'', ``The Rock Band Bush'', or just ``A Bush''. Associating a claim with a topic allows one to write shorter claims without worrying about being ambiguous. A topic can itself by disambiguated by having a super-topic.
\end{itemize}

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=8cm]{../screenshots/claimbrowse_diagram.png}
	\caption{The claim browser visualizes the claim graph}
	\label{claimbrowse_diagram}
	\end{center}
\end{figure}

@@

After several design iterations, we settled on an interface that is a dynamically reorganizing graph laid out like an outliner. Like other dynamically reorganizing graphs, the interface is arranged around the currently selected node, and when a new node is selected the interface animates to surround the newly selected node with objects to relate to it. Like an outliner, the nodes that relate to the selected node are listed vertically below the selected node, each on their own line, and grouped by category.

@@

\begin{figure}[tb]
	\begin{center}
	\includegraphics[width=6cm]{../screenshots/claimbrowse_zoom.png}
	\caption{Close up of a list of supporting claims}
	\label{claimbrowse_zoom}
	\end{center}
\end{figure}

@@

Users see a claim browser in three different places. The {\it organizer} contains two claim browsers, to help users use drag and drop to create connections (Figure~\ref{fig:claimbrowser}). The {\it popup browser} shows one claim browser in a reduced-size window and is used to quickly investigate a claim found on a web page (Figure~\ref{claimview}). The {\it claim selector} shows a claim browser, together with the text of a new snippet, and is used to identify the claim that a snippet is making (Figure~\ref{snipsavecrop}).

@@

There are several reasons a user may wish to add a snippet to Think Link. They may find the snippet useful and may want to refer to it again in the future; they may disagree with the claim the snippet is making, and want to alert other readers to the fact that there are opposing arguments; they may think the claim argues a point well and want to be able to use it to make an argument, or they may agree with the claim and want to provide easy access to evidence elsewhere that backs it up.

@@

Since much of Think Link's utility comes from linking snippets together, it is important to encourage users to reuse existing claims rather than creating new ones, and that when users do create new claims they connect them to existing claims and existing topics. We designed the claim selection window to make it easier to pick out an existing claim than to create a new one. Moreover, one cannot create a new claim without connecting it to an existing topic or an existing claim. To create a new claim, one navigates to a topic that the claim is about, or a claim that the new claim supports or opposes, and then clicks on the (\includegraphics[width=0.3cm]{../images/add.png}) button on the list that one wishes to add the new claim to. For example, if the new claim opposes an existing claim, then one clicks the (\includegraphics[width=0.3cm]{../images/add.png}) button on the ``opposed by'' heading for the existing claim. This is an intentionally different model to that used by ad-hoc tag-based systems such as Del.icio.us and Flickr.com. This is because in bookmarking or image storing systems it is not so important that duplicates be avoided and that objects be well connected. In practice, it is inevitable that duplicates claims and topics will sometimes be created. When this happens, a user can mark them as being identical using the same techniques used to create supporting and opposing connections.

@@

Like Wikipedia~\cite{wikipedia}, Think Link allows any user to improve the information in the claim graph. The claim graph is shared between all users and editable by anyone. Any user can add new snippets, create new claims, create new topics, or establish new relationships between these objects. One can think of Think Link as being rather like a wiki in which all the content is clipped from existing sources and links are created from those sources back to the wiki.

@@

In a wiki, users edit and delete information produced by others, and history is used to revert abusive changes. Think Link's ``append-only, collaborative filtering'' approach only allows users to add information --- either new objects, or ratings for those objects. The hope is that over time ratings should converge to a steady state and edit wars should be avoided. It would not be practical for a wiki to take this approach as wiki data is human-readable text, rather than a weighted graph; indeed Think Link has to fall back to the ``edit and keep history'' approach to allow users to rename claims.

@@

Our user study participants identified several reasons why they would want to mark up factual claims in documents they found. The most common reason people gave for identifying and organizing factual claims was if the person was writing an article or researching a topic and wanted to keep track of the information they had found. One user (who is an active blogger) also expressed an interest in finding and marking up instances of claims that he disagreed with, so that readers would see the arguments highlighted in red and be directed to the counter-arguments. The same user also expressed an interest in marking up claims in documents he had made in his own articles so that readers could quickly see the evidence he had found in support of his claims.

@@

For the second study, we recruited 6 paid participants. Four were female and two were male. Although we recruited participants using the same advert as the first study, the timing of our second advert around the beginning of the college semester meant that five of the participants were students. Since the second group was different demographically to the first group, it was not possible to make a direct comparison between their behaviors.

In the second study we were more confident about the usability of our tool and so we decided to tell them nothing about how to use it. We gave each user a brief introduction to the aims of the tool, similar to the introduction of this paper, and then asked them to perform two tasks with it. The first task was to look at a selection of web pages that already had highlighted snippets and explore the interface while thinking aloud about what they saw. The second task was to identify claims on a set of pages we gave them about global warming and connect them appropriately to existing claims that we had pre-populated the claim graph with. Participants were shown an interface that is largely identical to that described earlier in this paper.

@@

Users would often encounter a snippet that could be interpreted as making several interesting claims, and were unsure about what to do in such circumstances. Some users would deal with this by writing a compound claim like ``Global Warming will cause X and Y'' while other users would create several snippets for the same text, making different claims. Users seemed to find this confusing, suggesting that we may want support in the snippet creation interface for picking several claims that a snippet is making.

@@

For the second study, we used the snippet creation interface described earlier in this paper, which uses the same claim browser interface used for exploring the claim graph. We found that users of this interface had no difficulty distinguishing between claims and topics and were more likely to reuse existing claims and topics. We theorized that part of the reason for increased reuse was that, because users could see the claim graph they were creating, they felt more motivation to keep it ``tidy'' by reusing existing claims.

@@

Think Link is designed to be used as a social tool in which large numbers of people collaborate to find large numbers of claims and snippets about interesting topics. Since our graph and user base are currently small, we have not yet evaluated how Think Link works when data sets are huge, many users are concurrently editing data, and some users are malicious.
